Incorporating periodic variability in hidden Markov models for animal movement

### 2016-07-27 paper3.Rnw
cheesy paragraph

>>>>

On a broad spectrum, it really depends on what kind of question 
that is being answered. On one side of the spectrum, if the goal is 
to identify states, it might be sufficient to use a 
simple/traditional HMM model and pre-specify the number of states and, post hoc, 
match Viterbi-based states estimates with environmental variation 
\citep{fryxell_multiple_2008}. On the other side of the 
spectrum, if the goal of interest is to make predictions (out of sample), 
it might be better to fit a covariate-dependent model so that we can explicitly
model the switching process. In that case, fitting a covariate-dependent model is
better for out of sample prediction because Viterbi can only estimate state 
occupancy if observed movements are available (within sample preditions). 
Finally, if we want to estimate the number of states, BIC is not necessarily 
good for estimation of number of states \citep{biernacki2000assessing}, 
but it can be useful as an approximate upper limit estimate.

\section{Conclusion}
